The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-25 project/paper/properties.tex
Added explanation for the origins of the skew-normal.

@@

  An unfortunate consequence of this choice, however, is the misconception that
  $\mu$ and $\sigma$ are related to the mean and variance the way they are in
  the normal distribution. In the case of the skew-normal, it is more
  productive to think of them as abstract location and scale parameters. In
  fact, a quick comparison of figures \ref{fig:comparison-n25},
  \ref{fig:comparison-n50}, and \ref{fig:comparison-n100} and the corresponding
  parameters in Table \ref{tab:sn-approx-table} shows that $\mu$ and $\sigma$
  are not visually related to the curve in any intuitive way.}

\end{defn}

The skew-normal was first introduced by \citet{o'hagan} and was most notably
developed by \citet{azzalini-1985}.

@@

\begin{proof}
  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
  we restate here:

  \begin{helper-lem}
    If $f_0$ is a one-dimensional probability density function symmetric about
    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
    and is a density symmetric about 0, then

    \begin{equation}
      \label{eq:azzalini-perturbation-invariance}
      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
    \end{equation}

    is a density function for any odd function $w(\cdot)$.
  \end{helper-lem}

  This lemma is extended by a corollary which gives a very helpful result for
  the above defined $f_0$ and $f$:

  \begin{helper-cor}[Perturbation Invariance]
    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
    notation $\overset{d}{=}$ denotes equality in distribution.    
  \end{helper-cor}

  Let $X \sim N(0,1)$. Take $f_0 = \phi$, and $G = \Phi$. Then, $f_Z(z) = 2
  \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $X$ and
  $Z$ are equal in distribution.

>>>>

\label{subsec:foundations}

@@

  An unfortunate consequence of this choice, however, is the misconception that
  $\mu$ and $\sigma$ are related to the mean and variance the way they are in
  the normal distribution. In the case of the skew-normal, it is more
  productive to think of them as abstract location and scale parameters. In
  fact, a quick comparison of figures \ref{fig:comparison-n25},
  \ref{fig:comparison-n50}, and \ref{fig:comparison-n100} and the corresponding
  parameters in Table \ref{tab:sn-approx-table} shows that $\mu$ and $\sigma$
  are not visually related to the curve in any intuitive way.}
\end{defn}

The skew-normal was first introduced by \citet{o'hagan} and was most notably
developed by \citet{azzalini-1985}. It belongs to a class of skewed
distributions conforming to the following guidelines:

\begin{lem}
  \label{lem:azzalini-lemma-1}

  If $f_0$ is a one-dimensional probability density function symmetric about
  0, and $G$ is a one-dimensional distribution function such that $G'$ exists
  and is a density symmetric about 0, then

  \begin{equation}
    \label{eq:azzalini-skewed-distribution}
    f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
  \end{equation}

  is a density function for any odd function $w(\cdot)$. (Lemma 1,
  \citealp{azzalini})
\end{lem}

In equation \eqref{eq:azzalini-skewed-distribution}, $f_0$ acts as a weighting
function referred to as a kernel. When $f_0 = \phi$, the distribution is said
to be generated by the normal kernel. $G$ does not necessarily have to be taken
from the same distribution as $f_0$; for example, the normal kernel has been
paired with cdf's from various other distributions, such as Student's t,
Cauchy, Laplace, and uniform. In the case of our skew-normal, however, both
$f_0$ and $G$ come from the normal distribution.

@@

\begin{proof}
  Lemma \ref{lem:azzalini-lemma-1} from section \ref{subsec:foundations}
  provides a very useful result for the above defined $f_0$ and $f$, which we
  restate here as a corollary:

  \begin{cor}[Perturbation Invariance]
    \label{eq:azzalini-perturbation-invariance}

    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
    notation $\overset{d}{=}$ denotes equality in distribution. (Page 161,
    \citealp{azzalini})
  \end{cor}

  Let $X \sim N(0,1)$. Take $f_0 = \phi$, and $G = \Phi$. Then, $f_Z(z) = 2
  \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
  \eqref{eq:azzalini-skewed-distribution}, and we can conclude that $X$ and $Z$
  are equal in distribution.
